Superabsorption of light by nanoparticles

### 2015-07-22 2015-Ladutenko-Qabs/2015-Ladutenko-Qabs-ilya-v3.tex
Clean up

% \title{More efficient than a ``super'' absorption in spherical
% nanoparticles} %KSL
% \title{Super-absorption and efficient absorption of light by
% spherical nanoparticles} %IVS
\title{Super absorption of light by nanoparticles} %AEM
% Proposed reviewers: Anatoly Zayats
% Andrea Alu
% Sergei Bozhevolnyi

@@

\begin{abstract}
  Nanoparticles have a fundamental limit as to how much light they can
  absorb. This limit is based on the finite number of modes excited
  inside the nanoparticle at a given wavelength and maximal absorption
  capacity per mode. The enhanced absorption can be achieved
  when each mode supported by the nanopartice absorbs light up to the
  maximum capacity. Using stochastic optimization algorithm, we design
  multi-layer nanoparticles, in which we can make several resonant
  modes overlap at the same frequency resulting in {\it
    super-absorption}.  We further introduce the {\it efficiency of
    the absorption} for a nanoparticle, which is the absorption normalized
  by the physical size of the particle, and show that efficient
  absorbers are not always operating in super-absorbing regime.
\end{abstract}

@@

Mie theory~\cite{Mie-1908}, which is over 100 years old, describes
interaction of electromagnetic waves with spherical particles. Mie
solution is still of great interest these days~\cite{Suzuki-2008,MacKowski-2012,Lerme-2000,Xu-2005,Li-2006,Gogoi-2010,Santiago-2011},
since it is one of the primary tools for analyzing wave scattering by
spherical objects. Further development of the Mie
theory~\cite{Yang-2003, Pena-scattnlay-2009} made it possible to apply
it to study the multi-layered spherical
particles~\cite{Sheehan-2013,Selmke-2012}.  Such particles have
various applications in cancer treatment~\cite{Zhang-2010,
  Hirsch-2003}, medical diagnostics~\cite{Allain-2002},
cloaking~\cite{Qui-2009, Semouchkina-2013, Ladutenko-2014} and
plasmonic devices~\cite{Martin-2013, Alu-2005}, in the study of thermal properties of insulating materials~\cite{Xie-2013}, as well as for improving solar cells performance~\cite{Kameya-2011,Mann-2011}.

The scattering properties of multilayer cylinders and spheres was
studied in great detail by Ruan and Fan~\cite{Fan-2010,Fan-2011}.  In
these works authors introduced the concept of a super-scattering, when
the scattering cross-section of a multilayer particle exceeds that of
a homogeneous particle of the same size in the so-called
single-channel limit. The super-scattering appears when a
multi-layer structure has several nearly degenerate modes,
i.e. their resonance frequencies coincide or close to each other. In a homogeneous particle, the resonances appear at different frequencies, and there is no design freedom to make these resonances overlap, and this limits the
achievable scattering cross-section.

Similar fundamental limitations exist for the absorbing properties of
sub-wavelength nanoparticles.  Tribelsky~\cite{Tribelsky-2011} has
derived a theoretical limit of a maximum absorption cross-section
(ACS) value for a single channel, i.e., when only one mode of the
sphere is excited.  As a result the absorption coefficients
$\tilde{a}_n= {\rm Re}\{a_n\} - |a_n|^2 $ and $\tilde{b}_n= {\rm
  Re}\{b_n\} - |b_n|^2 $ become limited by $1/4$, here $a_n$ and $b_n$
are scattering coefficient as defined within the Mie
theory~\cite{Bohren-1983}.

To overcome these limitations, we employ similar approach to the one used for
enhancing absorption cross-section~\cite{Fan-2011}. In particular, we
propose to use the multi-layer structures, and by means of stochastic
optimization algorithm we optimize the ACS of such nanoparticles. We
analyze the absorption cross-section of these particles, and present
the super-absorption regime. We further introduce the absorption
efficiency, which is the ACS normalized to the geometric cross-section
of the particles. Here we show that there is a strong counter-play
between the increased absorption for larger particles vs size for
smaller particles, and quite remarkably we find that the most {\em
  efficient} absorption can be achieved in a single channel limit for
small particles.

Another approach for an ideal absorber is given in a recent work by
Grigoriev et al.~\cite{Grigoriev-2015}. Authors considered only
a dipole approximation, and the final result is very close to the dipole limit predicted by
Tribelsky~\cite{Tribelsky-2011}.  Such absorption design
corresponds to the single mode limit.  At the same time, Grigoriev et
al.~\cite{Grigoriev-2015} also provide an equation to design a
core-shell structure from given materials. However, in the case of
$Si$ core and $Ag$ shell materials and sizes taken from the best design obtained in the present paper, their equation gives a complex value for the core material filling factor, which cannot be achieved in an experimental realisations.

@@

We start our analyses by considering the triple layered $Si/Ag/Si$
spherical particle illuminated with a plane
wave schematically shown in Fig.~\ref{fig:geom}. In what follows we describe the materials
using experimentally measured parameters from the
Ref.~\cite{palik-1997}, and, e.g. at $\lambda = 500$ nm $\epsilon_{Si} = 18.5 + i0.63$ and
$\epsilon_{Ag} = -8.5 + i0.76$.  To optimize the thickness of each
layer we implemented~\cite{JADE-web} an adaptive differential
evolution algorithm~\cite{Storn-DE-first-1997}, which is called
JADE~\cite{Jingqiao-JADE-2009}.  The technical details of the
optimization algorithm are published previously in
Ref.~\cite{Ladutenko-2014}. We perform Mie calculations using the
Scattnlay software~\cite{Pena-scattnlay-2009,Scattnlay-web}, whose
results are verified by a number of other implementations of the
Mie solutions and by a commercially available software including CST
Microwave studio~\cite{CST-web} and Comsol Multiphysics~\cite{Comsol-web}.

It is a common understanding that, in general, a bigger particle 
has a bigger absorption cross-section, so sphere with the diameter of
1 cm absorbs more light than any nanoscale sphere. Therefore, it is practical to employ {\em the absorption
efficiency} $Q_{\rm abs}=C_{\rm abs}/\pi R^2$, where $R$ is the outer
radius of the particle and $C_{\rm abs}$ is the absorption
cross-section.

\begin{figure}
  \center{
    % Use pdfcrop to remove white margins
    \includegraphics[width=0.4\textwidth]{fig/2015-04-01-Qabs-SiAgSi-overview}%
    \caption{ Results of the optimization of the absorption efficiency
      for the fixed wavelength of 500~nm. (a) Absorption efficiency
      with the best value achieved for the particle of the radius of 36~nm and
      Ag/Si design (zero sized core). Dashed lines show theoretical
      limits for the first channel and second channel
      absorption. Second and third peaks in the absorption efficiency
      curve exceed the theoretical limit for the second mode
      absorption at $R=63$~nm and $R=81$~nm. Local maxima of
      absorption efficiency are additionally marked with arrows. (b) Mie absorption
      coefficients for individual excited modes of the optimized
      structures. (c) Optimized layer thicknesses. For the total
      particle radius below 46~nm the optimizer converges to
      the two-layer structure, when core size vanishes, and the
      optimum design is a bi-layer $Ag/Si$ particle. 
      \label{fig:overview}
    }%
  }
\end{figure}
%
In order to study the dependence of the absorption efficiency on the
outer particle size, we run optimization algorithm for different
(fixed) particle outer size, and our optimization parameters are the
radii of internal cores, whereas the target function is the absorption
efficiency. We maximize absorption efficiency at a fixed wavelength
of the incident light (we have chosen $\lambda=500$~nm). We show the results of our stochastic optimization
algorithm in Fig.~\ref{fig:overview}~(a).  Dashed lines show
theoretical absorption limit of a dipole ($n=1$) and a quadrupole
($n=2$) resonances~\cite{Tribelsky-2011}, which are given
as $$Q^{(n)}_{\rm abs\ max}=\frac{2n+1}{2q^2},$$ where the size
parameter $q=2\pi R/\lambda$, and $n$ is the angular momentum of the
mode. Following Ref.~\cite{Fan-2011}, where authors introduce
super-scattering for spherical particles, here we we introduce
super-absorption regime, when {\em the ACS is larger than the theoretical limit
for absorption by the mode with highest excited angular momentum
$n$}. In our parameter space we have just modes up to the quadrupole
excited ($n=2$), and in order to get a super-absorption our efficiency
should be higher than that of a quadrupole. We clearly see this
super-absorption regime at $R>60$~nm, in Fig.~\ref{fig:overview}~(a).

In Fig.~\ref{fig:overview}~(b) we present the values of Mie absorption
coefficients for individual excited modes in the structure, while
horizontal dashed line shows the theoretical limit (1/4) for each of
them. $\tilde{a}_{1,2}$ are electric dipole and electric quadrupole,
while $\tilde{b}_{1,2}$ are magnetic dipole and magnetic
quadrupole. For small particles, as expected, the absorption is
dominated by an electric dipole $\tilde{a}_1$.  At $R > 56.6$~nm the
optimization procedure finds that the designs with both electric and
magnetic dipoles have larger ACS, than the structure with only the
electric dipole excited. This is why the curves in
Figs.~\ref{fig:overview}~(b,c) experience the discontinuity. We also
note that there is a very narrow range of particle sizes, between
80.7~nm and 82.1~nm, where our analyses finds that the design
supporting electric dipole $\tilde{a}_1$ and magnetic quadrupole
$\tilde{b}_2$ has larger ACS, and this explains two more
discontinuities of the curves at the respective size values.

Fig.~\ref{fig:overview}~(c) shows optimized sizes of the layers inside
the multi-layer structure. It reveals quite a curious result, that the
dipole branch (i.e. for particle radii below 56.6~nm) has two
parts. For $R<46$~nm the best absorber has just two layers, as the
radius of the core of the three-layer structure vanishes, and the
particle reduces to $Ag/Si$ core-shell structure.  At $R=46$~nm dipole
channel reaches its theoretical limit (it becomes
$\tilde{a}_1>0.249$).  It appears that the optimizer introduced the
inner $Si$ layer in order to keep $\tilde{a}_1$ near the theoretical
limit as the $R$ increases.  As a side effect, the quadrupole
contribution $\tilde{a}_2$ appears; however, it does not help to reach
super-absorption limit for $n=2$.

Remarkably, the absolute maximum {\em absorption efficiency} is not reached
within the super-absorption regime. Figure~\ref{fig:overview} shows
that the maximum efficiency is achieved for small particle size, and
the ACS is still well below the single channel limit. It appears that
the $Ag/Si$ core-shell nanoparticle, with the total radii of
approximately 36~nm is the most efficient absorber in the considered
structure, whose ACS reaches values {\em over 5 times the physical
cross-section area of the particle}.  From practical point of view it
is quite important that the maximum can be reached in a bi-layer
structure, instead of a triple-layer, since it should be easier and
cheaper to fabricate.

\begin{figure}
  \center{
    % Use pdfcrop to remove white margins
    \includegraphics[width=0.4\textwidth]{fig/2015-04-01-SiAgSi-ab-spectra3.pdf}%
    \caption{Spectra of Mie absorption coefficients of (a) efficient and (b-c)super-absorption design.      
      \label{fig:spectra}
    }%
  }
\end{figure}
To study spectral properties of the structures with large ACS which we
obtained by the optimization, in Fig.~\ref{fig:spectra} we plot three
different cases for designs that correspond to local maxima of $Q_{\rm
  abs}$ shown in Fig.~\ref{fig:overview}~(a).  As expected, the design
corresponding to the maximum absorption efficiency at $R=36$~nm has a
single electric dipole resonance centered at the target wavelength
$\lambda=500$~nm. Spectra of designs with maxima at $R=63$~nm and
$R=81$~nm have a signature of the super-absorption, i.e. there is an
overlap of several resonances.  We note that these structures have
additional absorption resonances, but they are located far from the
wavelength of interest.

A noticeable feature of Fig.~\ref{fig:spectra}~(c) is an almost flat
top of the electric dipole resonance.  
%This effect might be related with the coupling between the electric
%dipole $\tilde{a}_1$ with the magnetic quadrupole $\tilde{b}_2$, but
%this hypothesis should be further tested.  Whereas resonant responses
%of other designs originate from coupling of incident plane wave with
%the corresponding multipole, it is not the case for the design with
%$R=81$~nm. Here, the particle is mostly composed from the $Si$ outer
%shell, that give enough volume for $\tilde{b}_2$.  Dipole response
%comes from the small inner part of the sphere and can not be directly
%excited with the incident wave.  It takes the power from the
%surrounding $\tilde{b}_2$ mode and very soon it reaches the
%fundamental limit for absorption.  This way, we can observe a flat top
%for the $\tilde{a}_1$ response accompanied with a significant value of
%$\tilde{b}_2$.  Our suggestion is indirectly proven by the reduced
%width of the $\tilde{b}_2$ resonance compared to other quadrupole
%responses.

\begin{figure}
  \center{
    % Use pdfcrop to remove white margins
    \includegraphics[width=0.45\textwidth]{fig/SiAgSi-flow-R62-YZ-Eabs.pdf}%
    \caption{ Amplitude of electric field for $R=36$~nm (a,c) and
      super-absorbing designs (b,d) in E-k  (a-b) and H-k (c-d)
      planes normalized to incident wave. 
      \label{fig:field}
    }%
  }
\end{figure}
Finally, we present distribution of the amplitude of the electric
field in Fig.~\ref{fig:field} for two designs: with the best
efficiency at $R=36$~nm and in a super-absorbing design with
$R=63$~nm.  Using semi-transparent white curves we also plot
streamlines of the Poynting vector which characterize energy flow.
For the effective design of the absorber, the power from a large
cross-sectional area flows into the particle.  In case of
super-absorption regime, we observe the formation of vortices in the
power flow, which make absorption more efficient as the
electromagnetic energy propagates several times through the absorbing
materials.  The reason for the smaller overall absorption efficiency
of a super-absorbing design is obvious: spatial distribution of the electric
field is not uniform inside the particle and the share of the volume
with high absorption rate in the vortices do not compensate low
absorption efficiency in the regions with small electric field (
absorbed power is expressed as $P_{\rm abs}=\frac{1}{2}\int\sigma
\left|E\right|^2dx\,dy\,dz$)

In conclusion, we introduce and study the effect of the super-absorption, when the
absorption cross-section of the nanoparticle can reach the theoretical
limit for several modes at the same frequency. This becomes possible when several resonant modes of the
structure overlap at the same frequency, and this regime can be achieved in multi-layer nanoparticles. Moreover, quite unexpectedly we find that the most efficient absorbers, which are characterized by
enhanced absorption efficiencies, are smaller nanoparticles working in
a single mode regime. We present their spectral characteristics and
field structure.  The stochastic algorithm utilized in our approach is
very generic and the optimization can be repeated for any desired
wavelength or wavelength range.  As a result, one can design
spectrally-selective absorbers or broadband absorbers with almost
arbitrary prescribed properties.  It is interesting to note
that a similar conclusion was made by Miller et al.~\cite{Miller-2014}
for extinction of arbitrary particles: small size with only dipole
response is preferable for geometric volume normalized efficiency.

\begin{acknowledgments}

 AEM and IVS would like to acknowledge support from the Australian Research Council through Future Fellow and Discovery project schemes. 
  % The authors would like to thank the Ministry of Education and
  % Science of the Russian Federation (Goszadanie 2014/190, Zadanie
  % No. 3.561.2014/K, project 14.584.21.0009 10), Russian Foundation
  % for Basic Research (Grant 15-02-01344), and Government of the
  % Russian Federation (Grant 074-U01) for the financial support. The
  % simulations of cloak designs has been funded by the Russian
  % Science Foundation Grant No. 14-12-01227.
\end{acknowledgments}

>>>>

% \title{More efficient than a ``super'' absorption in spherical
% nanoparticles} %KSL
% \title{Superabsorption and efficient absorption of light by
% spherical nanoparticles} %IVS
\title{Superabsorption of light by nanoparticles} %AEM
% Proposed reviewers: Anatoly Zayats Andrea Alu Sergei Bozhevolnyi

@@

\begin{abstract}
  Nanoparticles have a fundamental limit as to how much light they can
  absorb. This limit is based on the finite number of modes excited
  in the nanoparticle at a given wavelength and maximum absorption
  capacity per mode. The enhanced absorption can be achieved when each
  mode supported by the nanopartice absorbs light up to the maximum
  capacity. Using stochastic optimization algorithm, we design
  multilayer nanoparticles, in which we can make several resonant
  modes overlap at the same frequency resulting in {\it
    superabsorption}.  We further introduce the {\it efficiency of the
    absorption} for a nanoparticle, which is the absorption normalized
  by the physical size of the particle, and show that efficient
  absorbers are not always operating in the superabsorbing regime.
\end{abstract}

@@

Mie theory~\cite{Mie-1908}, which is over 100 years old, describes
interaction of electromagnetic waves with spherical particles. Mie
solution is still of great interest these
days~\cite{Suzuki-2008,MacKowski-2012,Lerme-2000,Xu-2005,Li-2006,Gogoi-2010,Santiago-2011},
since it is one of the primary tools for analyzing wave scattering by
spherical objects. Further development of the Mie
theory~\cite{Yang-2003, Pena-scattnlay-2009} made it possible to apply
it to the study of multilayer spherical
particles~\cite{Sheehan-2013,Selmke-2012}.  Such particles have
various applications in cancer treatment~\cite{Zhang-2010,
  Hirsch-2003}, medical diagnostics~\cite{Allain-2002},
cloaking~\cite{Qui-2009, Semouchkina-2013, Ladutenko-2014} and
plasmonic devices~\cite{Martin-2013, Alu-2005}, in the study of
thermal properties of insulating materials~\cite{Xie-2013}, as well as
for improving solar cells performance~\cite{Kameya-2011,Mann-2011}.

The scattering properties of multilayer cylinders and spheres was
studied in great detail by Ruan and Fan~\cite{Fan-2010,Fan-2011}.  In
these works the authors introduced the concept of superscattering,
when scattering cross-section of a multilayer particle exceeds that of
a homogeneous particle of the same size in the so-called
single-channel limit. Superscattering appears when a multilayer
structure has several nearly degenerate modes, i.e. their resonance
frequencies coincide or are close to each other. In a homogeneous
particle, resonances appear at different frequencies, and there is no
design freedom to make these resonances overlap, and this limits the
achievable scattering cross-section.

Similar fundamental limitations exist for the absorbing properties of
subwavelength nanoparticles.  Tribelsky~\cite{Tribelsky-2011} has
derived a theoretical limit of a maximum absorption cross-section
(ACS) value for a single channel, i.e., when only one mode of a sphere
is excited.  As a result, the absorption coefficients $\tilde{a}_n=
{\rm Re}\{a_n\} - |a_n|^2 $ and $\tilde{b}_n= {\rm Re}\{b_n\} -
|b_n|^2 $ become limited by $1/4$, here $a_n$ and $b_n$ are scattering
coefficient as defined within the Mie theory~\cite{Bohren-1983}.

To overcome these limitations, we employ similar approach to the one
used for enhancing scattering cross-section~\cite{Fan-2011}. In
particular, we propose to use the multilayer structures, and by means
of stochastic optimization algorithm we optimize the ACS of such
nanoparticles. We analyze the absorption cross-section of these
particles, and present the superabsorption regime. We further
introduce the absorption efficiency, which is the ACS normalized to
the geometric cross-section of particles. Here we show that there is a
strong counterplay between the increased absorption for larger
particles vs size for smaller particles, and quite remarkably we find
that the most {\em efficient} absorption can be achieved in a single
channel limit for small particles.

Another approach for an ideal absorber is given in the recent work by
Grigoriev et al.~\cite{Grigoriev-2015}. Authors considered only dipole
approximation, and the final result is very close to the dipole limit
predicted by Tribelsky~\cite{Tribelsky-2011}.  Such absorption design
corresponds to the single mode limit.  At the same time, Grigoriev et
al.~\cite{Grigoriev-2015} also provide an equation to design a
core-shell structure from given materials. However, in the case of
$Si$ core and $Ag$ shell materials and sizes taken from the best
design obtained in the present paper, their equation gives a complex
value for the core material filling factor, which cannot be achieved
in experimental realisations.

@@

We start our analyses by considering the triple-layer $Si/Ag/Si$
spherical particle illuminated with a plane wave schematically shown
in Fig.~\ref{fig:geom}. In what follows we describe the materials
using experimentally measured parameters from Ref.~\cite{palik-1997},
and, e.g. at $\lambda = 500$ nm $\epsilon_{Si} = 18.5 + i0.63$ and
$\epsilon_{Ag} = -8.5 + i0.76$.  To optimize the thickness of each
layer we implemented~\cite{JADE-web} an adaptive differential
evolution algorithm~\cite{Storn-DE-first-1997}, which is called
JADE~\cite{Jingqiao-JADE-2009}.  The technical details of the
optimization algorithm were published previously in
Ref.~\cite{Ladutenko-2014}. We perform Mie calculations using the
Scattnlay software~\cite{Pena-scattnlay-2009,Scattnlay-web}, whose
results are verified by a number of other implementations of the Mie
solutions and by commercially available software including CST
Microwave studio~\cite{CST-web} and Comsol
Multiphysics~\cite{Comsol-web}.

It is a common understanding that, in general, a larger particle has a
larger absorption cross-section, so sphere with the diameter of 1 cm
absorbs more light than any nanoscale sphere. Therefore, it is
practical to employ {\em the absorption efficiency} $Q_{\rm
  abs}=C_{\rm abs}/\pi R^2$, where $R$ is the outer radius of the
particle and $C_{\rm abs}$ is the absorption cross-section.

\begin{figure}
  \center{
    % Use pdfcrop to remove white margins
    \includegraphics[width=0.4\textwidth]{fig/2015-04-01-Qabs-SiAgSi-overview}%
    \caption{ Results of optimization of the absorption efficiency
      for the fixed wavelength of 500~nm. (a) Absorption efficiency
      with the best value achieved for the particle of the radius of 36~nm and
      Ag/Si design (zero sized core). Dashed lines show theoretical
      limits for the first channel and second channel
      absorption. The second and third peaks in the absorption efficiency
      curve exceed the theoretical limit for the second mode
      absorption at $R=63$~nm and $R=81$~nm. Local maxima of
      absorption efficiency are additionally marked with arrows. (b) Mie absorption
      coefficients for individual excited modes of the optimized
      structures. (c) Optimized layer thicknesses. For the total
      particle radius below 46~nm the optimizer converges to
      a bi-layer structure, when core size vanishes, and the
      optimum design is a $Ag/Si$ particle. 
      \label{fig:overview}
    }%
  }
\end{figure}
%
In order to study the dependence of the absorption efficiency on the
outer particle size, we run optimization algorithm for different
(fixed) particle outer size, and our optimization parameters are the
radii of internal cores, whereas the target function is the absorption
efficiency. We maximize absorption efficiency at a fixed wavelength of
the incident light (we have chosen $\lambda=500$~nm). We show the
results of our stochastic optimization algorithm in
Fig.~\ref{fig:overview}~(a).  Dashed lines show theoretical absorption
limit of a dipole ($n=1$) and a quadrupole ($n=2$)
resonances~\cite{Tribelsky-2011}, which are given as $$Q^{(n)}_{\rm
  abs\ max}=\frac{2n+1}{2q^2},$$ where the size parameter $q=2\pi
R/\lambda$, and $n$ is the angular momentum of the mode. Following
Ref.~\cite{Fan-2011}, where the authors introduce superscattering for
spherical particles, here we introduce superabsorption regime, when
{\em the ACS is larger than the theoretical limit for absorption by
  the mode with the highest excited angular momentum $n$}. In our
parameter space we have just modes up to the quadrupole excited
($n=2$), and in order to get superabsorption our efficiency should be
higher than that of a quadrupole. We clearly see this superabsorption
regime at $R>60$~nm, in Fig.~\ref{fig:overview}~(a).

In Fig.~\ref{fig:overview}~(b) we present the values of Mie absorption
coefficients for individual excited modes in the structure, while
horizontal dashed line shows the theoretical limit (1/4) for each of
them. $\tilde{a}_{1,2}$ are electric dipole and electric quadrupole,
while $\tilde{b}_{1,2}$ are magnetic dipole and magnetic
quadrupole. For small particles, as expected, absorption is dominated
by electric dipole $\tilde{a}_1$.  At $R > 56.6$~nm the optimization
procedure finds that the designs with both electric and magnetic
dipoles have larger ACS than the structure with only the electric
dipole excited. This is why the curves in
Figs.~\ref{fig:overview}~(b,c) experience the discontinuity. We also
note that there is a very narrow range of particle sizes, between
80.7~nm and 82.1~nm, where our analysis finds that the design
supporting electric dipole $\tilde{a}_1$ and magnetic quadrupole
$\tilde{b}_2$ has larger ACS, and this explains two more
discontinuities of the curves at the respective size values.

Fig.~\ref{fig:overview}~(c) shows optimized sizes of layers inside a
multilayer structure. It reveals quite a curious result, that the
dipole branch (i.e. for particle radii below 56.6~nm) has two
parts. For $R<46$~nm the best absorber has just two layers, as the
radius of the core of a triple-layer structure vanishes, and the
particle reduces to $Ag/Si$ core-shell structure.  At $R=46$~nm dipole
channel reaches its theoretical limit (it becomes
$\tilde{a}_1>0.249$).  It appears that the optimizer introduced the
inner $Si$ layer in order to keep $\tilde{a}_1$ near the theoretical
limit as the $R$ increases.  As a side effect, the quadrupole
contribution $\tilde{a}_2$ appears; however, it does not help to reach
superabsorption limit for $n=2$.

Remarkably, the absolute maximum {\em absorption efficiency} is not
reached within the superabsorption regime. Figure~\ref{fig:overview}
shows that the maximum efficiency is achieved for small particle size,
and the ACS is still well below the single channel limit. It appears
that the $Ag/Si$ core-shell nanoparticle with the total radii of
approximately 36~nm is the most efficient absorber among the considered
structures, whose ACS reaches values {\em over 5 times the physical
  cross-section area of the particle}.  From a practical point of view,
it is quite important that the maximum can be reached in a bi-layer
structure, instead of a triple-layer, since it should be easier and
cheaper to fabricate.

\begin{figure}
  \center{
    % Use pdfcrop to remove white margins
    \includegraphics[width=0.4\textwidth]{fig/2015-04-01-SiAgSi-ab-spectra4.pdf}%
    \caption{Spectra of Mie absorption coefficients of (a) efficient and (b-c)superabsorption design. Panel (d) shows the superposition of the squared absolute values of the Mie coefficients for electric dipole contribution inside each layer. 
      \label{fig:spectra}
    }%
  }
\end{figure}
To study spectral properties of structures with large ACS which we
obtained by the optimization, in Fig.~\ref{fig:spectra} we plot three
different cases for designs that correspond to local maxima of $Q_{\rm
  abs}$ shown in Fig.~\ref{fig:overview}~(a).  As expected, the design
corresponding to the maximum absorption efficiency at $R=36$~nm has a
single electric dipole resonance centered at the target wavelength
$\lambda=500$~nm. Spectra of designs with maxima at $R=63$~nm and
$R=81$~nm have a signature of the superabsorption, i.e. there is an
overlap of several resonances.  We note that these structures have
additional absorption resonances, but they are located far from the
wavelength of interest.  A noticeable feature of
Fig.~\ref{fig:spectra}~(c) is an almost flat top of the electric
dipole resonance. More detailed analysis shows that we have {\em excited several electric dipole resonances} with close resonance frequencies within our multilayer structure. Indeed, if we plot a superposition of the squares of the absolute values of the Mie coefficients, which characterize energy stored in each layer, we find that we excite resonances in all three layers, and they are slightly offset as shown in Fig.~\ref{fig:spectra} (d). Combined effect of these resonances produces the flat and relatively broadband electric resonance response shown in Fig.~\ref{fig:spectra} (c).

\begin{figure}
  \center{
    % Use pdfcrop to remove white margins
    \includegraphics[width=0.45\textwidth]{fig/SiAgSi-flow-R62-YZ-Eabs.pdf}%
    \caption{ Amplitude of electric field for $R=36$~nm (a,c) and
      superabsorbing designs (b,d) in E-k  (a-b) and H-k (c-d)
      planes normalized to incident wave. 
      \label{fig:field}
    }%
  }
\end{figure}
Finally, we present distribution of the amplitude of the electric
field in Fig.~\ref{fig:field} for two designs: with the best
efficiency at $R=36$~nm and in a superabsorbing design with $R=63$~nm.
Using semi-transparent white curves we also plot streamlines of the
Poynting vector which characterize energy flow.  For the effective
design of the absorber, the power from a large cross-sectional area
flows into the particle.  In case of superabsorption regime, we
observe the formation of vortices in the power flow, which make
absorption more efficient as the electromagnetic energy propagates
several times through the absorbing materials.  The reason for the
smaller overall absorption efficiency of a superabsorbing design is
obvious: spatial distribution of the electric field is not uniform
inside the particle and the share of the volume with high absorption
rate in the vortices does not compensate low absorption efficiency in
the regions with small electric field (absorbed power is expressed as
$P_{\rm abs}=\frac{1}{2}\int\sigma \left|E\right|^2dx\,dy\,dz$)

In conclusion, we introduce and study the effect of superabsorption,
when the absorption cross-section of the nanoparticle can reach the
theoretical limit for several modes at the same frequency. This
becomes possible when several resonant modes of the structure overlap
at the same frequency, and this regime can be achieved in multilayer
nanoparticles. Moreover, quite unexpectedly we find that the most
efficient absorbers, which are characterized by enhanced absorption
efficiencies, are smaller nanoparticles working in a single mode
regime. We present their spectral characteristics and field structure.
The stochastic algorithm utilized in our approach is very generic and
the optimization can be repeated for any desired wavelength or
wavelength range.  As a result, one can design spectrally-selective
absorbers or broadband absorbers with almost arbitrary prescribed
properties.  It is interesting to note that a similar conclusion was
made by Miller et al.~\cite{Miller-2014} for extinction of arbitrary
particles: small size with only dipole response is preferable for
geometric volume normalized efficiency.

\begin{acknowledgments}
  Thanks to David A. Powell for his contribution to the analysis of
  the spectrum feature.  AEM and IVS would like to acknowledge support
  from the Australian Research Council through Future Fellow and
  Discovery project schemes. KSL and PAB would like to thank the
  Ministry of Education and Science of the Russian Federation and
  Government of the Russian Federation (Grant 074-U01) for the
  financial support.
\end{acknowledgments}
